### 2014-10-20 PAPER_AMMLY.tex
Some more tuning

\begin{theorem}
Let $\mathcal{N}$, whose output is $Y_{\Lambda}$, be the neural network predicting $1$ with probability $p$ and $-1$ otherwise. Let $\mathcal{M}$ be its $(s,\epsilon)$-reduction image for some $s \leq \Lambda$ and $\epsilon \in [0,1]$. Then
\[corr(sign(Y_s),sign(Y_{\Lambda})) \geq \frac{2p(1 \!-\! p \!+\! \epsilon) \!-\! \epsilon}{2\sqrt{(p \!+\! \epsilon)(1 \!-\! p \!+\! \epsilon)p(1 \!-\! p)}},
\]
where $corr$ denotes the correlation defined as $corr(A,B) = \frac{\mathbb{E}[(A - \mathbb{E}[A]])(B - \mathbb{E}[B]])}{std(A)std(B)}$, $std$ is the standard deviation and $sign(\cdot)$ denotes the sign of prediction ($sign(Y_s)$ and $sign(Y_{\Lambda})$ are both random).
\label{thm:redun}
\end{theorem}

@@

\begin{theorem}
Under the uniformity assumption of Equation~\ref{eq:uniform}, random variable $\hat{Y}_s$ in Equation~\ref{eq:approx} and random variable $Y_{\Lambda}$ in Equation~\ref{eq:befapprox} sattisy the following
\[corr(\hat{Y}_s,Y_{\Lambda}) \geq \sqrt{\frac{1-\delta}{1+\delta}}.
\]
\label{thm:unif}
\end{theorem}

@@

\section{Proof of Theorem~\ref{thm:redun}}
\begin{proof}
Consider two random variables $Z_s = sign(Y_s)$ and $Z_{\Lambda} = sign(Y_{\Lambda})$, where the first one considers the sign of prediction of network $\mathcal{N}$ and the latter considers the sign of prediction of network $\mathcal{M}$. Let $\mathcal{X}^{+}$ denote the set of data points for which $\mathcal{N}$ predicts $+1$ and let $\mathcal{X}^{-}$ denote the set of data points for which $\mathcal{N}$ predicts $-1$ ($\mathcal{X}^{+} \cup \mathcal{X}^{-} = \mathcal{X}$, where $\mathcal{X}$ is the entire dataset). Also let $p = \frac{|\mathcal{X}^{+}|}{|\mathcal{X}|}$. Furthermore, let $\mathcal{X}_{\epsilon}^{-}$ denote the dataset for which $Z_{\Lambda} = +1$ and $Z_s = -1$ and $\mathcal{X}_{\epsilon}^{+}$ denote the dataset for which $Z_{\Lambda} = -1$ and $Z_s = +1$, where $\frac{|\mathcal{X}_{\epsilon}^{+}| + |\mathcal{X}_{\epsilon}^{-}|}{\mathcal{X}} = \epsilon$. Also let $\epsilon^{+} = \frac{|\mathcal{X}_{\epsilon}^{+}|}{\mathcal{X}}$ and $\epsilon^{-} = \frac{|\mathcal{X}_{\epsilon}^{-}|}{\mathcal{X}}$. Therefore
\[Z_{\Lambda} \!=\! \left \{
  \begin{tabular}{c}
  $1$ \:\:if $x \in \mathcal{X}^{+}$\\
  \!\!\!\!$-1$ \:\:if $x \in \mathcal{X}^{-}$
  \end{tabular}
\right.
\]
and
\[Z_s \!=\! \left \{
  \begin{tabular}{c}
  $1$ \:\:if $x \in \mathcal{X}^{+} \cup \mathcal{X}_{\epsilon}^{+}  \setminus \mathcal{X}_{\epsilon}^{-}$\\
  \!\!\!$-1$ \:\:if $x \in \mathcal{X}^{-} \cup \mathcal{X}_{\epsilon}^{-} \setminus \mathcal{X}_{\epsilon}^{+}$.
  \end{tabular}
\right.
\]
One can compute that $\mathbb{E}[Z_{\Lambda}] = 2p-1$, $\mathbb{E}[Z_s] = 2(p + \epsilon^{+} - \epsilon^{-}) - 1$, $\mathbb{E}[Z_sZ_{\Lambda}] = 1$, $std(Z_s) = 2\sqrt{p(p-1)}$, and finally $std(Z_\Lambda) = 2\sqrt{(p + \epsilon^{+} - \epsilon^{-})(p + \epsilon^{+} - \epsilon^{-} - 1)}$.
Thus we obtain
\begin{eqnarray*}
&&corr(sign(Y_s),sign(Y_{\Lambda})) = corr(Z_s,Z_{\Lambda})\\
&=& \frac{\mathbb{E}[Z_sZ_{\Lambda}] - \mathbb{E}[Z_s]\mathbb{E}[Z_{\Lambda}]}{std(Z_s)std(Z_{\Lambda})}\\
&=& \frac{1 - (2(p + \epsilon^{+} - \epsilon^{-}) - 1)(2p-1)}{4\sqrt{(p + \epsilon^{+} - \epsilon^{-})(p + \epsilon^{+} - \epsilon^{-} - 1)p(p-1)}}\\
&=& \frac{2p + 2(1-2p)(p + \epsilon^{+} - \epsilon^{-})}{4\sqrt{(p + \epsilon^{+} - \epsilon^{-})(1 - p - \epsilon^{+} + \epsilon^{-})p(1 - p)}}\\
&\geq& \frac{p + (1-2p)(p - \epsilon)}{2\sqrt{(p + \epsilon)(1 - p + \epsilon)p(1 - p)}}\\
&=& \frac{2p(1 - p + \epsilon) - \epsilon}{2\sqrt{(p + \epsilon)(1 - p + \epsilon)p(1 - p)}}\\
\end{eqnarray*}
\end{proof}

\section{Proof of Theorem~\ref{thm:redun}}
\begin{proof}
Note that $\mathbb{E}[\hat{Y}_s] = 0$ and $\mathbb{E}[Y_{\Lambda}] = 0$. Furthermore
\[\mathbb{E}[\hat{Y}_sY_{\Lambda}] = q^2\rho^2\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}}r_{i_1,i_2,\dots,i_H}\prod_{k = 1}^{H}w_{i_k}^2
\]
and
\[std(\hat{Y}_s) = q\rho\sqrt{\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\frac{\Psi}{\Lambda^H}\prod_{k = 1}^{H}w_{i_k}^2}
\]
\[std(Y_{\Lambda}) = q\rho\sqrt{\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}r_{i_1,i_2,\dots,i_H}^2\prod_{k = 1}^{H}w_{i_k}^2}.
\]
Therefore
\begin{eqnarray*}
&&\!\!\!\!\!\!\!\!\!corr(\hat{Y}_s,Y_{\Lambda})\\ 
&\!\!\!\!\!\!\!\!\!=&\!\!\!\!\!\!\! \frac{\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}}r_{i_1,\dots,i_H}\prod_{k = 1}^{H}w_{i_k}^2}{\sqrt{\!\!\!\left(\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\frac{\Psi}{\Lambda^H}\prod_{k = 1}^{H}w_{i_k}^2\right)\!\!\!\!\left(\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\!\!\!\!\!r_{i_1,\dots,i_H}^2\prod_{k = 1}^{H}w_{i_k}^2\right)}}\\
&\!\!\!\!\!\!\!\!\geq& \sqrt{\frac{1-\delta}{1+\delta}}, 
\end{eqnarray*}
where the last inequality is the direct consequence of the uniformity assumption of Equation~\ref{eq:uniform}.
\end{proof}

>>>>

\begin{theorem}
Let $\mathcal{N}$, whose output is $Y_{\Lambda}$, be the neural network predicting $1$ with probability $p$ and $-1$ otherwise. Let $\mathcal{M}$ be its $(s,\epsilon)$-reduction image for some $s \leq \Lambda$ and $\epsilon \in [0,p]$. Then
\[corr(sign(Y_s),sign(Y_{\Lambda})) \geq \frac{2p(1 \!-\! p \!+\! \epsilon) \!-\! \epsilon}{2\sqrt{(p \!+\! \epsilon)(1 \!-\! p \!+\! \epsilon)p(1 \!-\! p)}},
\]
where $corr$ denotes the correlation defined as $corr(A,B) = \frac{\mathbb{E}[(A - \mathbb{E}[A]])(B - \mathbb{E}[B]])}{std(A)std(B)}$, $std$ is the standard deviation and $sign(\cdot)$ denotes the sign of prediction ($sign(Y_s)$ and $sign(Y_{\Lambda})$ are both random).
\label{thm:redun}
\end{theorem}

@@

\begin{theorem}
Under the uniformity assumption of Equation~\ref{eq:uniform}, random variable $\hat{Y}_s$ in Equation~\ref{eq:approx} and random variable $Y_{\Lambda}$ in Equation~\ref{eq:befapprox} sattisy the following
\[corr(\hat{Y}_s,Y_{\Lambda}) \geq \frac{1-\delta}{1+\delta}.
\]
\label{thm:unif}
\end{theorem}

@@

\section{Proof of Theorem~\ref{thm:redun}}
\begin{proof}
Consider two random variables $Z_s = sign(Y_s)$ and $Z_{\Lambda} = sign(Y_{\Lambda})$, where the first one considers the sign of prediction of network $\mathcal{N}$ and the latter considers the sign of prediction of network $\mathcal{M}$. Let $\mathcal{X}^{+}$ denote the set of data points for which $\mathcal{N}$ predicts $+1$ and let $\mathcal{X}^{-}$ denote the set of data points for which $\mathcal{N}$ predicts $-1$ ($\mathcal{X}^{+} \cup \mathcal{X}^{-} = \mathcal{X}$, where $\mathcal{X}$ is the entire dataset). Also let $p = \frac{|\mathcal{X}^{+}|}{|\mathcal{X}|}$ and without loss of generality assume $p \leq 0.5$. Furthermore, let $\mathcal{X}_{\epsilon}^{-}$ denote the dataset for which $Z_{\Lambda} = +1$ and $Z_s = -1$ and $\mathcal{X}_{\epsilon}^{+}$ denote the dataset for which $Z_{\Lambda} = -1$ and $Z_s = +1$, where $\frac{|\mathcal{X}_{\epsilon}^{+}| + |\mathcal{X}_{\epsilon}^{-}|}{\mathcal{X}} = \epsilon$. Also let $\epsilon^{+} = \frac{|\mathcal{X}_{\epsilon}^{+}|}{\mathcal{X}}$ and $\epsilon^{-} = \frac{|\mathcal{X}_{\epsilon}^{-}|}{\mathcal{X}}$. Therefore
\[Z_{\Lambda} \!=\! \left \{
  \begin{tabular}{c}
  $1$ \:\:if $x \in \mathcal{X}^{+}$\\
  \!\!\!\!$-1$ \:\:if $x \in \mathcal{X}^{-}$
  \end{tabular}
\right.
\]
and
\[Z_s \!=\! \left \{
  \begin{tabular}{c}
  $1$ \:\:if $x \in \mathcal{X}^{+} \cup \mathcal{X}_{\epsilon}^{+}  \setminus \mathcal{X}_{\epsilon}^{-}$\\
  \!\!\!$-1$ \:\:if $x \in \mathcal{X}^{-} \cup \mathcal{X}_{\epsilon}^{-} \setminus \mathcal{X}_{\epsilon}^{+}$.
  \end{tabular}
\right.
\]
One can compute that $\mathbb{E}[Z_{\Lambda}] = 2p-1$, $\mathbb{E}[Z_s] = 2(p + \epsilon^{+} - \epsilon^{-}) - 1$, $\mathbb{E}[Z_sZ_{\Lambda}] = 1$, $std(Z_s) = 2\sqrt{p(p-1)}$, and finally $std(Z_\Lambda) = 2\sqrt{(p + \epsilon^{+} - \epsilon^{-})(p + \epsilon^{+} - \epsilon^{-} - 1)}$.
Thus we obtain
\begin{eqnarray*}
&&corr(sign(Y_s),sign(Y_{\Lambda})) = corr(Z_s,Z_{\Lambda})\\
&=& \frac{\mathbb{E}[Z_sZ_{\Lambda}] - \mathbb{E}[Z_s]\mathbb{E}[Z_{\Lambda}]}{std(Z_s)std(Z_{\Lambda})}\\
&=& \frac{1 - (2(p + \epsilon^{+} - \epsilon^{-}) - 1)(2p-1)}{4\sqrt{(p + \epsilon^{+} - \epsilon^{-})(p + \epsilon^{+} - \epsilon^{-} - 1)p(p-1)}}\\
&=& \frac{2p + 2(1-2p)(p + \epsilon^{+} - \epsilon^{-})}{4\sqrt{(p + \epsilon^{+} - \epsilon^{-})(1 - p - \epsilon^{+} + \epsilon^{-})p(1 - p)}}\\
&\geq& \frac{p + (1-2p)(p - \epsilon)}{2\sqrt{(p + \epsilon)(1 - p + \epsilon)p(1 - p)}}\\
&=& \frac{2p(1 - p + \epsilon) - \epsilon}{2\sqrt{(p + \epsilon)(1 - p + \epsilon)p(1 - p)}}\\
\end{eqnarray*}
\end{proof}

\section{Proof of Theorem~\ref{thm:redun}}
\begin{proof}
Note that $\mathbb{E}[\hat{Y}_s] = 0$ and $\mathbb{E}[Y_{\Lambda}] = 0$. Furthermore
\[\mathbb{E}[\hat{Y}_sY_{\Lambda}] = q^2\rho^2\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}}r_{i_1,i_2,\dots,i_H}\prod_{k = 1}^{H}w_{i_k}^2
\]
and
\[std(\hat{Y}_s) = q\rho\sqrt{\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\frac{\Psi}{\Lambda^H}\prod_{k = 1}^{H}w_{i_k}^2}
\]
\[std(Y_{\Lambda}) = q\rho\sqrt{\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}r_{i_1,i_2,\dots,i_H}^2\prod_{k = 1}^{H}w_{i_k}^2}.
\]
Therefore
\begin{eqnarray*}
&&\!\!\!\!\!\!\!\!\!corr(\hat{Y}_s,Y_{\Lambda})\\ 
&\!\!\!\!\!\!\!\!\!=&\!\!\!\!\!\!\! \frac{\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}}r_{i_1,\dots,i_H}\prod_{k = 1}^{H}w_{i_k}^2}{\sqrt{\!\!\!\left(\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\frac{\Psi}{\Lambda^H}\prod_{k = 1}^{H}w_{i_k}^2\right)\!\!\!\!\left(\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\!\!\!\!\!r_{i_1,\dots,i_H}^2\prod_{k = 1}^{H}w_{i_k}^2\right)}}\\
&\!\!\!\!\!\!\!\!\geq& \frac{1-\delta}{1+\delta}, 
\end{eqnarray*}
where the last inequality is the direct consequence of the uniformity assumption of Equation~\ref{eq:uniform}.
\end{proof}
